A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.

@@

In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ for different redshifts and metallicities. 
In the top panel we

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. From now on, we will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial \SFRDzZ model. 
% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.

@@

In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities. 
In the top panel we show the general trend of the \SFRDzZ linear in lookback time.

Main results:

1) We did a pretty good job at fitting the data. 
In general, the skewed-log normal metallicity distribution does a good job at capturing the metallicity dependent star formation in TNG. 
We did miss some features like the almoast dubble peak at redshift 2,

Adopting a skewed-lognormal distribution furthermore allows for a tail of low metallicity star formation

0) the starformation rate peaks at metallicities above $10^{-2}$ for all redshifts out to at least $z=6$
most star formation happens at metallicities above $Z \gtr 10^{-2}$

% Things to say about this plot: 
We recognise some of the features discussed in \cite{Pakmor+2022}
We make a comparison to Neijssel fiducial: their model is extremely narrow, while the metallicity in the TNG is more broad
